Title

### 2023-05-09 main.tex
refuckulated the carbonator

\begin{figure}
\centering
\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
\caption{Algunos colores posibles }
\end{figure}

@@

% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of fig.~(\ref{fig: circuit-pauli}). However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in eq. (\ref{eq: parametrized state}).

In general, producing this curve of states will require multiple rotations
parametrized by $p$. For instance, in the case of a two-qubit curve of states,
we would typically need three rotations that depend on $p$, s
imilar to those illustrated for the ancilla qubits in fig. (\ref{fig: circuit-pauli-1}).
Moreover, creating an $N$-qubit curve of states
usually necessitates $N-1$ parametrized rotations.

However, it is desirable to minimize the number of parametrized rotations in our circuit.
This leads us to the following question: which curves of states,
such as the one described in eq. (\ref{eq: parametrized state}), 
can be generated using only a single parametrized rotation? 
To clarify this, we provide the following definition for a circuit with one parametrized rotation.

\begin{definition}{\textbf{OPR Circuit:}}
An OPR (One-Parameterized Rotation) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}

Based on this definition, we aim to determine which curves of 
states can be generated using OPR circuits. 
To accomplish this, we begin by proving that any OPR circuit exhibits 
a specific form, as stated in the following theorem.

\begin{theorem}
An $N-$qubit OPR circuit can always be transformed into the form shown in
fig.~(\ref{fig:OPR-circuit}).
\end{theorem}

\begin{figure}[h!]
\centering
\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of an OPR circuit}.
Any OPR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter}
\label{fig:OPR-circuit}
\end{figure}

\textbf{Proof:} 
First, we observe that according to the
definition, an OPR circuit always consists of an operation $B$ followed 
by the parametrized rotation and then another operation $A$, 
where $A$ and $B$ are not parametrized.

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any OPR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the target qubit for the rotation.

Therefore, an OPR circuit can be transformed such
that the rotation is around $\sigma_3$ and is applied to the last qubit 
(possibly controlled by other qubits), 
resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). $\blacksquare$ \\
$\;$\\

@@

\begin{theorem}
An OPR circuit always implements an operator whose matrix,
in the computational basis, has the form:
\begin{eqnarray}
U = (|\vec{v}_0|, |\vec{v}_1|, |\vec{v}_2|, \cdots, |\vec{v}_{2^n-1}|),
\end{eqnarray}
where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
Using Theorem 1, we know that any OPR circuit can be transformed into the 
form shown in Figure (\ref{fig:OPR-circuit}).
Hence, we only need to consider the operator corresponding to that circuit. 
The $j$-th column of the circuit's matrix represents the result of applying the circuit to the state $|j\rangle$.

@@

Therefore, from this theorem we conclude that
the kind of curves of states that can be created
using an OPR circuit are always of the form
\begin{align*}
|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
\end{align*}
where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
\newpage
% }}}
\section{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\tbnote{Sección no escrita aún, sólo es el medio resumen que tenía.}
We can now use the last theorem to conclude directly which Pauli dynamical maps
can be created using an OPR circuit.
For OPR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for OPR circuits implies that a map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} \cos s + \vec{b} \sin s
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

@@

%\textbf{Puntos:}
%\begin{itemize}
%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
%\end{itemize}
% }}}
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita. Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$. Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis. 
\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
\begin{itemize}
\item Cualquier matriz $H$ de un qubit cumple el teorema.
\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
\end{itemize}
\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
\end{itemize}
% }}}
\section{Conclusion} % {{{

>>>>

\begin{figure}
\centering
\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
\caption{Algunos colores posibles. Creo qeu me gustaria usar otra candidad, 
como la fidelidad, pero definida a partir de la norma diamante. 
Asi, 1 es perfecto y 0 esta mal. De estas, me gusta la de abajo 
a la izquiera porque siento que distingue bien, pero si toca entnoces
usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
propongo tambien que se ponta la leyenda en la figura y no encima. 
Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ.  }
\end{figure}

@@

% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
\cpnote{No se sabe aun que son OPR circuits. Poner completo}

Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of fig.~(\ref{fig: circuit-pauli}). However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in \eref{eq: parametrized state}.
\cpnote{me gusta mas usar el comando eref para que si toca cambiarlo, dependiendo 
de la revista, lo pueda hacer de un solo jalon. Lo mismo para las 
figuras.}

In general, producing this curve of states will require multiple rotations
parametrized by $p$. For instance, in the case of a two-qubit curve of states,
we would typically need three rotations that depend on $p$, similar to those
illustrated for the ancilla qubits in \fref{fig: circuit-pauli-1}.
Moreover, creating an $N$-qubit curve of states
usually necessitates $N-1$ parametrized rotations.
\cpnote{no me salen esas cuentas.}

However, it is desirable to minimize the number of parametrized rotations in our circuit.
\cpnote{why?}
This leads us to the following question: which curves of states,
such as the one described in \eref{eq: parametrized state}, 
can be generated using only a single parametrized rotation? 
To clarify this, we provide the following definition for a circuit with one parametrized rotation.
\cpnote{Creo qeu los dos párrafos anteriores son uno y toca pensar cual es el
mensaje principal y rediseñar. }

\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}

Based on this definition, we aim to determine which curves of 
states can be generated using OPR \cpnote{Si te parece bien el cambio 
en la sigla, cambialos todos} circuits. 
To accomplish this, we begin by proving that all OPR circuit have 
a specific form.

\begin{figure} % {{{
\centering
\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of an OPR circuit}.
Any OPR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.
\cpnote{Parece que se te olvida la puntuacion en algunos captions. 
por otro lado, queda la figura a mitad de la prueba. A mi me gusta dejar 
que Latex organice solo las figuras y sin ponerle el h! ni nada. }
}
\label{fig:OPR-circuit}
\end{figure} % }}}

\begin{theorem}
An $N-$qubit OPR circuit can always be transformed into the form shown in
fig.~(\ref{fig:OPR-circuit}).
\end{theorem}
\textbf{Proof:} 
First, we observe that according to the
definition, an OPR circuit always consists of an operation $B$ followed 
by the parametrized rotation and then another operation $A$, 
where $A$ and $B$ are not parametrized.

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any OPR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation \cpnote{Why?}.

Therefore, an OPR circuit can be transformed such
that the rotation is around $\sigma_3$ and is applied to the last qubit 
(possibly controlled by other qubits), 
resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). 
\cpnote{Creo que este ultimo parrafo sobra, aunque hay detalles aca que quizá se pueden
poner en el planteamiento del problema.}
$\blacksquare$ \\
$\;$\\

@@

\begin{theorem}
An OPR circuit always implements an operator whose matrix,
in the computational basis, has the form:
\begin{eqnarray}
U = (|\vec{v}_0|, |\vec{v}_1|, |\vec{v}_2|, \cdots, |\vec{v}_{2^n-1}|),
\end{eqnarray}
\cpnote{que denota el valor absoluto?}
where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
\cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
Using Theorem 1, we know that any OPR circuit can be transformed into the 
form shown in Figure (\ref{fig:OPR-circuit}).
Hence, we only need to consider the operator corresponding to that circuit. 
The $j$-th column of the circuit's matrix represents the result of applying the circuit to the state $|j\rangle$.

@@

Therefore, from this theorem we conclude that
the kind of curves of states that can be created
using an OPR circuit are always of the form
\begin{align*}
|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
\end{align*}
where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
\newpage
% }}}
\section{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}

\tbnote{Sección no escrita aún, sólo es el medio resumen que tenía.}
We can now use the last theorem to conclude directly which Pauli dynamical maps
can be created using an OPR circuit.
For OPR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for OPR circuits implies that a map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} \cos s + \vec{b} \sin s
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

@@

%\textbf{Puntos:}
%\begin{itemize}
%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
%\end{itemize}
% }}}
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}
\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita. Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$. Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis. 
\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
\begin{itemize}
\item Cualquier matriz $H$ de un qubit cumple el teorema.
\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
\end{itemize}
\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
\end{itemize}
% }}}
\section{Conclusion} % {{{
